Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-09-18 ms/ms.Rmd
qualitative site descriptions

Introduction text goes here.
You can change the name of the section if necessary using `\introduction[modified heading]`.

@@

## Subsection Heading Here

Read Gatis et al. [-@gatisMappingUplandPeat2019] 
and related work [@minasnyDigitalMappingPeatlands2019].

### Subsubsection Heading Here

>>>>

Introduction text goes here.
Read Gatis et al. [-@gatisMappingUplandPeat2019] and related work [@minasnyDigitalMappingPeatlands2019].

@@

## Sites

We assessed how well we could predict peat depth at two sites with conspicuously different physical geography: Skrimfjella in eastern Norway and Ørskogfjellet in western Norway (*insert figure ref*).
These sites were chosen because they were covered by radiometric data from airborne surveys, relatively little built-up area, and road access.

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility.   
The landscape within our delineation is classified as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land dataset, \unit{1.5\,km^{2}} (4.5 %) of the study area is classified as peatland.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey. 
This study area comprises a wide range of major landscape types: *coastal plains*, *coastal fjord*, *inland valleys*, as well as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 data set counts \unit{15.3\,km^{2}} (12.4 %) of the study area as peatland.

## Measuring peat depth

### Skrimfjella

### Ørskogfjellet

### 2024-09-18 ms/ms.tex
qualitative site descriptions

Introduction text goes here.
You can change the name of the section if necessary using \texttt{\textbackslash{}introduction{[}modified\ heading{]}}.

@@

\subsection{Subsection Heading Here}

Read Gatis et al. \citeyearpar{gatisMappingUplandPeat2019}
and related work \citep{minasnyDigitalMappingPeatlands2019}.

\subsubsection{Subsubsection Heading Here}

>>>>

Introduction text goes here.
Read Gatis et al. \citeyearpar{gatisMappingUplandPeat2019} and related work \citep{minasnyDigitalMappingPeatlands2019}.

@@

\subsection{Sites}

We assessed how well we could predict peat depth at two sites with conspicuously different physical geography: Skrimfjella in eastern Norway and Ørskogfjellet in western Norway (\emph{insert figure ref}).
These sites were chosen because they were covered by radiometric data from airborne surveys, relatively little built-up area, and road access.

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility.\\
The landscape within our delineation is classified as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land dataset, \unit{1.5\,km^{2}} (4.5 \%) of the study area is classified as peatland.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey.
This study area comprises a wide range of major landscape types: \emph{coastal plains}, \emph{coastal fjord}, \emph{inland valleys}, as well as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 data set counts \unit{15.3\,km^{2}} (12.4 \%) of the study area as peatland.

\subsection{Measuring peat depth}

\subsubsection{Skrimfjella}

\subsubsection{Ørskogfjellet}
